Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-23 paper.tex
Experiment Results Update
Work in progress.

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig_fun_ackley.pdf}
    \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions comparison.} \label{fig.fun_ackley}
    \end{figure}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Ackley Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.benchmark_fun_ackley5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Ackley Function - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.69E-08 & 1.36E-08 & 46,331 & 49.9 \\
    \textbf{Elite Projection} & 6.33E-08 & 2.70E-08 & 13,811 & 18.1 \\
    \textbf{All Random} & 6.78E-08 & 2.55E-08 & 30,236 & 32.8 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Ackley Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.benchmark_fun_ackley10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Ackley Function - 10 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 9.35E-08 & 5.93E-09 & 104,842 & 111.7 \\
    \textbf{Elite Projection} & 5.11E-08 & 3.13E-08 & 16,019 & 20.1 \\
    \textbf{All Random} & 6.89E-08 & 2.75E-08 & 43,631 & 46.3 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

\subsection{Experiment Configuration}

For each experiment, we ran 60 independent executions per algorithm and
recorded the following results: Last Generation, Total Evaluations, Time
(seconds), Evaluations/second. The labels used on the results of our summarized
experiments tables are the following:

\begin{itemize}
    \item   Last Gen.   is the generation that found the solution.
    \item   Eval.       is the total number of evaluations the algorithm executed. 
    \item   Time (sec)  is the total elapsed or wall clock time, in seconds. 
    \item   Eval/sec    is the calculated rate of evaluations per second.
\end{itemize}

>>>>

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig_fun_ackley.pdf}
    \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_ackley}
    \end{figure}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Ackley Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_ackley5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Ackley Function - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.69E-08 & 1.36E-08 & 46,331 & 49.9 \\
    \textbf{Elite Projection} & 6.33E-08 & 2.70E-08 & 13,811 & 18.1 \\
    \textbf{All Random} & 6.78E-08 & 2.55E-08 & 30,236 & 32.8 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Ackley Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_ackley10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Ackley Function - 10 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 9.35E-08 & 5.93E-09 & 104,842 & 111.7 \\
    \textbf{Elite Projection} & 5.11E-08 & 3.13E-08 & 16,019 & 20.1 \\
    \textbf{All Random} & 6.89E-08 & 2.75E-08 & 43,631 & 46.3 \\ \bottomrule
    \end{tabular}
    \end{table}

\subsubsection{Bohachevsky Benchmark Function Experiment}

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig_fun_bohachevsky.pdf}
    \caption{Box and whisker chart for the Bohachevsky Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_bohachevsky}
    \end{figure}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Bohachevsky Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_bohachevsky5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Bohachevsky - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 7.28E-08 & 2.20E-08 & 15,010 & 24.2 \\
    \textbf{Elite Projection} & 4.51E-08 & 2.94E-08 & 8,266 & 12.6 \\
    \textbf{All Random} & 6.16E-08 & 2.85E-08 & 11,998 & 21.7 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Bohachevsky Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_bohachevsky10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Bohachevsky - 10   Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.66E-08 & 1.38E-08 & 40,166 & 44.4 \\
    \textbf{Elite Projection} & 3.80E-08 & 3.34E-08 & 8,506 & 12.9 \\
    \textbf{All Random} & 5.34E-08 & 3.76E-08 & 19,537 & 26.8 \\ \bottomrule
    \end{tabular}
    \end{table}

\subsubsection{Griewank Benchmark Function Experiment}

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig_fun_griewank.pdf}
    \caption{Box and whisker chart for the Griewank Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_griewank}
    \end{figure}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Griewank Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_griewank5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Griewank - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 6.92E-08 & 2.40E-08 & 44,566 & 48.3 \\
    \textbf{Elite Projection} & 3.77E-08 & 2.74E-08 & 16,412 & 20.1 \\
    \textbf{All Random} & 5.63E-08 & 2.99E-08 & 35,761 & 38.5 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Griewank Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_griewank10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Griewank - 10 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.07E-08 & 1.39E-08 & 92,885 & 100.0 \\
    \textbf{Elite Projection} & 4.21E-08 & 3.40E-08 & 13,534 & 17.3 \\
    \textbf{All Random} & 5.08E-08 & 3.54E-08 & 40,544 & 52.5 \\ \bottomrule
    \end{tabular}
    \end{table}

\subsubsection{Rastrigin Benchmark Function Experiment}

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig_fun_rastrigin.pdf}
    \caption{Box and whisker chart for the Rastrigin Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_rastrigin}
    \end{figure}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Rastrigin Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rastrigin5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Rastrigin - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 7.85E-08 & 1.59E-08 & 22,322 & 34.1 \\
    \textbf{Elite Projection} & 4.42E-08 & 3.26E-08 & 10,860 & 14.8 \\
    \textbf{All Random} & 5.66E-08 & 2.81E-08 & 21,122 & 35.0 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Rastrigin Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rastrigin10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Rastrigin - 10   Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.56E-08 & 1.23E-08 & 53,579 & 58.7 \\
    \textbf{Elite Projection} & 3.17E-08 & 2.57E-08 & 8,704 & 13.0 \\
    \textbf{All Random} & 5.00E-08 & 3.16E-08 & 24,376 & 27.4 \\ \bottomrule
    \end{tabular}
    \end{table}

\subsubsection{Sphere Benchmark Function Experiment}

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig_fun_sphere.pdf}
    \caption{Box and whisker chart for the Sphere Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_sphere}
    \end{figure}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Sphere Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_sphere5}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Sphere - 5 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 7.82E-08 & 1.65E-08 & 11,312 & 14.5 \\
    \textbf{Elite Projection} & 3.60E-08 & 3.27E-08 & 7,056 & 10.9 \\
    \textbf{All Random} & 6.14E-08 & 2.79E-08 & 9,158 & 12.2 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering
    \caption{Sphere Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_sphere10}
    \begin{tabular}{@{}lllll@{}}
    \toprule
    \multicolumn{5}{l}{\textbf{Function Sphere - 10 Dimensions}} \\ \midrule
     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
    \textbf{Xover Mutation} & 8.39E-08 & 1.45E-08 & 30,769 & 34.4 \\
    \textbf{Elite Projection} & 4.28E-08 & 3.06E-08 & 9,236 & 13.3 \\
    \textbf{All Random} & 5.32E-08 & 3.38E-08 & 21,465 & 26.3 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

\subsection{Experiment Example}
